Poll-Based Forecasting of the 2024 U.S. Presidential Election

### 2024-11-04 paper/paper.qmd
install_pacakges updated
install_pacakges updated

---
title: "Forecasting the 2024 U.S. Presidential Election: Comparative Support Analysis of Kamala Harris and Donald Trump"
subtitle: "Predictive Models Indicate a Narrow Advantage for Harris in a Closely Contested Race"
author: 
  - Haowei Fan
  - Fangning Zhang
  - Shaotong Li
thanks: "Code and data are available at: [https://github.com/HaoweiFan0912/US_Election-Forecast/tree/main]."
date: today
date-format: long
abstract: "This study aggregates polling data to forecast support for 2024 U.S. presidential candidates Kamala Harris and Donald Trump. By applying linear models with adjustments, we identify a modest lead for Harris at 47.6% over Trump’s 43.5%. The findings highlight that carefully weighted polling data provides a clearer view of electoral dynamics, showing how rigorous methodology in forecasting can yield more accurate insights into public opinion trends, aiding informed decision-making in political and economic spheres."
format: pdf
toc: true           
toc-title: "Table of Contents" 
toc-depth: 2    
number_sections: true    
bibliography: references.bib
---
```{r}
#| include: false
#| warning: false
#| message: false
#| echo: false
#### Workspace setup ####
library(tidyverse)
library(knitr)
library(dplyr)
library(arrow)
library(patchwork)
library(car)
library(kableExtra)
library(gridExtra)
library(moments)
library(grid)
set.seed(912)
#### Read data ####
raw_data <- read_csv(here::here("data/01-raw_data/raw_data.csv"))
train_Trump <- read_parquet(here::here("data/02-analysis_data/01-training/train_Trump.parquet"))
train_Harris <- read_parquet(here::here("data/02-analysis_data/01-training/train_Harris.parquet"))
test_Trump <- read_parquet(here::here("data/02-analysis_data/02-testing/test_Trump.parquet"))
test_Harris <- read_parquet(here::here("data/02-analysis_data/02-testing/test_Harris.parquet"))
full_Trump <- read_parquet(here::here("data/02-analysis_data/00-full/full_Trump.parquet"))
full_Harris <- read_parquet(here::here("data/02-analysis_data/00-full/full_Harris.parquet"))
Trump_model <- readRDS(here::here("models/Trump_model.rds"))
Harris_model <- readRDS(here::here("models/Harris_model.rds"))
```

# Introduction
The U.S. presidential election has profound implications on a global scale, shaping international relations, economic policy, and key social issues. As the 2024 election approaches, the ability to accurately forecast potential outcomes is essential for policymakers, businesses, and organizations seeking to anticipate shifts in U.S. policy that may affect trade, climate commitments, and strategic alliances [@citeBBC]. Additionally, recent analyses suggest that the election could introduce volatility into financial markets, emphasizing the importance of reliable predictions for strategic planning [@citeEuronews]. However, predicting election outcomes presents significant challenges due to a multitude of influencing factors, such as media influence, public sentiment, and socio-political dynamics, which collectively add complexity to election forecasting [@citeOregon]. Past elections further illustrate that targeted messaging and political events can profoundly impact voter behavior, complicating predictions even further [@citeYale].

@@

This paper is structured as follows: first, the data collection and filtering processes are outlined, followed by a description of the methodological framework, introducing linear modeling approaches. The results are then presented and analyzed, with a discussion on broader implications. The paper concludes with recommendations for future research and potential applications of these forecasting models in electoral studies.

This project leverages several R packages, including tidyverse[@citeTidyverse], janitor[@citeJanitor], tidyr[@citeTidyr], dplyr[@citeDplyr], lubridate[@citeLubridate], arrow[@citeArrow], patchwork[@citePatchwork], car[@citeCar], kableExtra[@citeKableExtra], gridExtra[@citeGridExtra], moments[@citeMoments], grid[@citeGrid], rstanarm[@citeRstanarm], and testthat[@citeTestthat], to clean, organize, analyze, and visualize data in forecasting voter support for the 2024 U.S. presidential election. These packages support a reproducible and rigorous approach to data management, statistical modeling, and result presentation, ensuring transparency and accuracy throughout the analysis process.
 【最后改结构描述加cross-reference】

@@

## Overview
The dataset comes from FiveThirtyEight's 'Presidential Election Polls (Current Cycle)' (Ryan Best and Wiederkehr, 2024). FiveThirtyEight is a well-known website recognized for its political, economic, and sports analyses. Its polling aggregation methodology is highly regarded in the field, aiming to provide readers with transparent, scientific, and as accurate as possible predictions. This polling data is compiled from various polling agencies, encompassing a wide range of demographic information, which serves as an essential basis for analyzing public voting preferences in the upcoming presidential election.

The analysis and visualizations in this paper are based on polling results as of October 22. The dataset includes 52 variables and 17,133 samples from various polling sources, asking participants who they support in the upcoming presidential election. To ensure accuracy and consistency, the data has been carefully processed and cleaned to remove biases and guarantee data integrity and comparability.

This project leverages several R packages, including tidyverse[@tidyverse], rstanarm[@rstanarm], testthat[@testthat], readr[@readr], broom[@broom], ggplot2[@ggplot2], and posterior[@posterior], to clean, analyze, and visualize polling data for the 2024 U.S. presidential election forecast. These packages facilitate a reproducible approach to data handling, statistical modeling, and result presentation in this study.

## Raw data
Raw data 一共包含了52个variable以及17133个sample.
```{r, fig.height=90, fig.width=90}
#| warning: false
#| message: false
#| echo: false
#| label: tbl-vord
#| tbl-cap: "Varibales of raw data"

# Get the column names and arrange them into multiple columns
column_names <- names(raw_data)
num_columns <- 3  # Set the desired number of columns
num_rows <- ceiling(length(column_names) / num_columns)
matrix_data <- matrix(c(column_names, rep("", num_columns * num_rows - length(column_names))), 
                      nrow = num_rows, byrow = TRUE)

# Convert the matrix to a data frame and format it with kable, set font size, and adjust header styling to remove extra row
kable(as.data.frame(matrix_data), 
      col.names = NULL)
```
其中重要的variables，其余的在appdendix
```{r, fig.height=90, fig.width=90}
#| warning: false
#| message: false
#| echo: false
#| label: tbl-ivatd
#| tbl-cap: "Important variables and their descriptions"

variable_descriptions <- data.frame(
  Variable = c("poll_id", "methodology", "population", "ranked_choice_reallocated",
               "hypothetical", "answer", "numeric_grade", "pollscore", 
               "transparency_score", "start_date", "end_date", "sample_size", "pct"),
  Description = c(
    "Unique identifier for each poll conducted.",
    "The method used to conduct the poll (e.g., Online Panel).",
    "The abbreviated description of the respondent group, typically indicating their voting status (e.g., 'lv' for likely voters).",
    "Indicates if ranked-choice voting reallocations have been applied in the results.",
    "Indicates whether the poll is about a hypothetical match-up.",
    "The response or answer choice given in the poll (e.g., the candidate's party).",
    "A numeric rating given to the pollster to indicate their quality or reliability (e.g., 3.0).",
    "A numeric value representing the score or reliability of the pollster in question (e.g., -1.1).",
    "A score reflecting the pollster's transparency about their methodology (e.g., 9.0).",
    "The date the poll began (e.g., 10/8/24).",
    "The date the poll ended (e.g., 10/11/24).",
    "The total number of respondents participating in the poll (e.g., 2712).",
    "The percentage of the vote or support that the candidate received in the poll (e.g., 51.0 for Kamala Harris)."
  )
)

# Create the table using kable
kable(variable_descriptions) %>%
  kable_styling() %>%
  column_spec(1, width = "4.5cm") %>% # Adjust the width of the first column
  column_spec(2, width = "10cm")    # Adjust the width of the second column
```
52个varibles中以下几个与我们的project明显无关，我们在此不做讨论：
"notes", "url", "url_article", "url_topline", "url_crosstab", "source"
```{r, fig.height=90, fig.width=90}
#| warning: false
#| message: false
#| echo: false
del_1 <- c("notes", "url", "url_article", "url_topline", "url_crosstab", "source")
droped_data <- raw_data %>% select(-any_of(del_1))
```
此外，还有一些相同的variables，我们保留其一，剩下的也不做讨论，它们包括："pollster", "sponsors", "display_name", "pollster_rating_name", "sponsor_candidate", "endorsed_candidate_name", "population_full", "candidate_id", "candidate_name"
```{r}
#| warning: false
#| message: false
#| echo: false
# 这里需要画一个table，展示删除的重复变量
del_2 <- c("pollster", "sponsors", "display_name", "pollster_rating_name", "sponsor_candidate", "endorsed_candidate_name",
           "population_full", "candidate_id", "candidate_name")
droped_data <- droped_data %>% select(-any_of(del_2))
```
常数变量我们也不做讨论，因为无法影响我们的预测，它们是：
```{r, fig.height=90, fig.width=90}
#| warning: false
#| message: false
#| echo: false
#| label: tbl-cv
#| tbl-cap: "Constant variables"
# Identify variables where all values are the same (including NA)
same_value_variables <- names(droped_data)[sapply(droped_data, function(x) length(unique(x)) == 1)]
# Create a data frame with variables and their unique values
same_value_data <- data.frame(Variable = same_value_variables, Value = sapply(same_value_variables, function(var)
unique(na.omit(droped_data[[var]]))[1]))
# Print the names of variables with all identical values using kable
kable(same_value_data[, 2, drop = FALSE], col.names = c("Variable", "Value"))
del_4 <- c("endorsed_candidate_id", "endorsed_candidate_party", "subpopulation", "cycle", "election_date", "stage", "nationwide_batch", 
           "office_type", "seat_number", "seat_name")
droped_data <- droped_data %>% select(-any_of(del_4))
```
其中categorical的有"poll_id", "pollster_id", "sponsor_ids", "pollster_rating_id", "methodology", "state",
         "sponsor_candidate_id", "sponsor_candidate_party", "question_id", "population", "tracking", "created_at", "internal",
         "partisan","race_id", "ranked_choice_reallocated", "ranked_choice_round", "hypothetical","party","answer"
```{r}
#| warning: false
#| message: false
#| echo: false
catego <- c("poll_id", "pollster_id", "sponsor_ids", "pollster_rating_id", "methodology", "state",
         "sponsor_candidate_id", "sponsor_candidate_party", "question_id", "population", "tracking", "created_at", "internal",
         "partisan","race_id", "ranked_choice_reallocated", "ranked_choice_round", "hypothetical","party","answer")
```
重要的categorical为下面的，剩下的将在appendix阐述："poll_id", "methodology", "population", "ranked_choice_reallocated", "hypothetical","answer"
```{r}
#| warning: false
#| message: false
#| echo: false
catego_inp <- c("poll_id", "methodology", "population", "ranked_choice_reallocated", "hypothetical","answer")
```
一共有3530个poll
```{r}
#| warning: false
#| message: false
#| echo: false
# Get unique Poll IDs and print the count
unique_poll_ids <- unique(raw_data$poll_id)
```
描述
```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-bv
#| fig-cap: "Boolean variables"

# Bar chart for 'ranked_choice_reallocated' with count labels
plots[["ranked_choice"]] <- ggplot(raw_data, aes(x = ranked_choice_reallocated)) +
  geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
  geom_text(stat = "count", aes(label = after_stat(count)), vjust = -0.5, size = 4) +  # Updated count label notation
  labs(title = "Bar Chart of Ranked Choice Reallocated", x = "Ranked Choice Reallocated", y = "Count") +
  theme_minimal(base_size = 15) +
  theme(
    plot.title = element_text(hjust = 0.5, size = 12),
    axis.title = element_text(size = 10),
    axis.text = element_text(size = 10)
  ) +
  ylim(0, max(table(raw_data$ranked_choice_reallocated)) * 1.2)  # Increase y-axis limit to fit labels

# Bar chart for 'hypothetical' with count labels
plots[["hypothetical"]] <- ggplot(raw_data, aes(x = hypothetical)) +
  geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
  geom_text(stat = "count", aes(label = after_stat(count)), vjust = -0.5, size = 4) +  # Updated count label notation
  labs(title = "Bar Chart of Hypothetical", x = "Hypothetical", y = "Count") +
  theme_minimal(base_size = 15) +
  theme(
    plot.title = element_text(hjust = 0.5, size = 12),
    axis.title = element_text(size = 10),
    axis.text = element_text(size = 10)
  ) +
  ylim(0, max(table(raw_data$hypothetical)) * 1.2)  # Increase y-axis limit to fit labels

# Combine and print the plots using patchwork
combined_plot <- wrap_plots(plots, ncol = 2) +
  plot_annotation(
    theme = theme(
      plot.title = element_text(hjust = 0.5, size = 14)
    )
  )

# Print the combined plot
print(combined_plot)

```
描述
```{r, fig.pos="H", fig.width=18, fig.height=18}
#| warning: false
#| message: false
#| echo: false
#| label: fig-cv
#| fig-cap: "Catogorical variables"

# Top 3 Methodologies with 'Other' grouped
methodology_counts <- sort(table(raw_data$methodology), decreasing = TRUE)
top_3_methodologies <- names(methodology_counts)[1:3]
raw_data$methodology_grouped <- ifelse(raw_data$methodology %in% top_3_methodologies, raw_data$methodology, "Other")

# Create horizontal bar chart for 'methodology'
plots[["methodology"]] <- ggplot(raw_data, aes(x = methodology_grouped)) +
  geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
  geom_text(stat = "count", aes(label = after_stat(count)), hjust = -0.2, size = 9) +  # Larger count labels
  labs(title = "Top 3 Methodologies and Others", x = "Count", y = "Methodology") +
  theme_minimal(base_size = 24) +  # Increase base size for all text elements
  theme(
    plot.title = element_text(hjust = 0.5, size = 32, face = "bold"),  # Title font size
    axis.title = element_text(size = 28),  # Axis title font size
    axis.text = element_text(size = 24)  # Axis text font size
  ) +
  coord_flip()

# Population bar chart
plots[["population"]] <- ggplot(raw_data, aes(x = population)) +
  geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
  geom_text(stat = "count", aes(label = after_stat(count)), hjust = -0.2, size = 9) +  # Larger count labels
  labs(title = "Population", x = "Count", y = "Population") +
  theme_minimal(base_size = 24) +  # Increase base size for all text elements
  theme(
    plot.title = element_text(hjust = 0.5, size = 32, face = "bold"),  # Title font size
    axis.title = element_text(size = 28),  # Axis title font size
    axis.text = element_text(size = 24)  # Axis text font size
  ) +
  coord_flip()

# Top 3 Answers with 'Other' grouped
answer_counts <- sort(table(raw_data$answer), decreasing = TRUE)
top_3_answer <- names(answer_counts)[1:3]
raw_data$answer <- ifelse(raw_data$answer %in% top_3_answer, raw_data$answer, "Other")

# Create horizontal bar chart for 'answer'
plots[["answer"]] <- ggplot(raw_data, aes(x = answer)) +
  geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
  geom_text(stat = "count", aes(label = after_stat(count)), hjust = -0.2, size = 9) +  # Larger count labels
  labs(title = "Top 3 Answers and Others", x = "Count", y = "Answer") +
  theme_minimal(base_size = 24) +  # Increase base size for all text elements
  theme(
    plot.title = element_text(hjust = 0.5, size = 32, face = "bold"),  # Title font size
    axis.title = element_text(size = 28),  # Axis title font size
    axis.text = element_text(size = 24)  # Axis text font size
  ) +
  coord_flip()

# Combine the plots using patchwork
combined_plot <- wrap_plots(plots, ncol = 1) +
  plot_annotation(
    theme = theme(
      plot.title = element_text(hjust = 0.5, size = 32)
    )
  )

# Print the combined plot
print(combined_plot)

```
描述
```{r, fig.pos="H", fig.width=18, fig.height=18}
#| warning: false
#| message: false
#| echo: false
#| label: fig-donvp1
#| fig-cap: "Distribution of numerical varibales part 1"

### Create Plots for Numeric Variables ###
# Create a list to store plots
plots <- list()

# Loop through selected numeric variables and plot their distributions with a line connecting bar tops
for (variable in names(numer %>% select(numeric_grade, pollscore, transparency_score))) {
  # Calculate bin counts and midpoints
  bin_data <- ggplot_build(
    ggplot(raw_data, aes_string(x = variable)) +
      geom_histogram(binwidth = 0.5)
  )$data[[1]]

  # Calculate the midpoint of each bin for line plotting
  bin_data <- bin_data %>%
    mutate(midpoint = (xmin + xmax) / 2)

  # Create histogram plot with line connecting the bar tops
  plots[[variable]] <- ggplot(raw_data, aes_string(x = variable)) +
    geom_histogram(binwidth = 0.5, fill = "#69b3a2", color = "black", alpha = 0.8) +
    labs(title = paste("Distribution of", variable), x = variable, y = "Frequency") +
    theme_minimal(base_size = 24) +  # Adjusted base font size for readability
    theme(
      plot.title = element_text(hjust = 0.5, size = 35, face = "bold"),  # Larger title font size
      axis.title = element_text(size = 35),  # Axis title font size
      axis.text = element_text(size = 35)  # Axis text font size
    )
}

### Combine and Print Plots ###
# Combine all individual plots into one vertical layout
combined_plot <- wrap_plots(plots, ncol = 1) +
  plot_annotation(
    theme = theme(
      plot.title = element_text(hjust = 0.5, size = 35)
    )
  )

# Print the combined plot
print(combined_plot)

>>>>

---
title: "Poll-Based Forecasting of the 2024 U.S. Presidential Election"
subtitle: "Valid Multiple Linear Regression Explains Why Kamala Harris Will Win"
author: 
  - Haowei Fan
  - Fangning Zhang
  - Shaotong Li
thanks: "Code and data are available at: [https://github.com/HaoweiFan0912/US_Election-Forecast/tree/main]."
date: today
date-format: long
abstract: "The United States plays a major role in the global technological and economic landscape, with its political leadership having a significant influence on international technology cooperation and economic relations. This project uses multiple linear regression to predict the outcome of the 2024 U.S. presidential election by extracting and analyzing polling data from polls that nominated the same candidates, providing insights to help stakeholders prepare for potential shifts in U.S. policies. The project predicts that Kamala Harris will secure 47.6% of the vote over Donald Trump's 43.5% and presents a straightforward yet effective regression model that does not rely on time-series analysis or external events."
format: pdf
toc-depth: 2    
number-sections: true
toc: true           
toc-title: "Table of Contents" 
bibliography: references.bib
---
```{r}
#| include: false
#| warning: false
#| message: false
#| echo: false
#### Workspace setup ####
install.packages("tidyverse")
library(tidyverse)
install.packages("knitr")
library(knitr)
install.packages("dplyr")
library(dplyr)
install.packages("arrow")
library(arrow)
install.packages("patchwork")
library(patchwork)
install.packages("car")
library(car)
install.packages("kableExtra")
library(kableExtra)
install.packages("gridExtra")
library(gridExtra)
install.packages("moments")
library(moments)
install.packages("grid")
library(grid)
set.seed(912)
#### Read data ####
raw_data <- read_csv(here::here("data/01-raw_data/raw_data.csv"))
train_Trump <- read_parquet(here::here("data/02-analysis_data/01-training/train_Trump.parquet"))
train_Harris <- read_parquet(here::here("data/02-analysis_data/01-training/train_Harris.parquet"))
test_Trump <- read_parquet(here::here("data/02-analysis_data/02-testing/test_Trump.parquet"))
test_Harris <- read_parquet(here::here("data/02-analysis_data/02-testing/test_Harris.parquet"))
full_Trump <- read_parquet(here::here("data/02-analysis_data/00-full/full_Trump.parquet"))
full_Harris <- read_parquet(here::here("data/02-analysis_data/00-full/full_Harris.parquet"))
Trump_model <- readRDS(here::here("models/Trump_model.rds"))
Harris_model <- readRDS(here::here("models/Harris_model.rds"))
```

# Introduction
The United States, as a global leader in both the economy and technology, plays a crucial role in shaping international trade and technological development. The president of the U.S. has a significant impact on these domains, which in turn affects the entire world. For instance, when Donald Trump took office in 2016, his administration's economic sanctions against China resulted in significant consequences, including a loss of nearly 300,000 jobs in the U.S. and an estimated 0.3% decline in real GDP [@citeBrookings]. In contrast, President Obama’s Affordable Care Act (ACA) expanded healthcare access, enabling millions of Americans to obtain affordable health coverage and improving overall health security [@citeObamaACA]. Therefore, predicting the outcome of the U.S. presidential election on November 5, 2024, is crucial for stakeholders to strategically prepare for the global impact that the new president may bring.

@@

The structure of this report is as follows: The @sec-data provides an overview of the raw data's origin and includes visualizations of some key variables. Additionally, detailed steps for cleaning the data are explained in this section, and the measurement of the raw data is analyzed in depth. Similar datasets are also discussed here. The @sec-model includes a detailed description of the model, covering the estimators and estimand. It also explains why alternative models were not chosen and validates our final model. The @sec-result presents the main findings of our model. The @sec-discussion analyzes the effects of different variables on the predictions, discusses the model's limitations, and explores its implications for real-world applications. The @sec-appendix reviews the YouGov pollster methodology, explains how to create an ideal survey for predicting election outcomes, and includes visualizations of less important raw data.

In this project, We used R[@citeR] and several R packages for data processing, analysis, and visualization. Specifically, tidyverse[@citeTidyverse], arrow[@citeArrow], dplyr[@citeDplyr], tidyr[@citeTidyr], janitor[@citeJanitor], lubridate[@citeLubridate], and here[@citeHere] were used for data processing, cleaning, date and time operations, project path management, and efficient data storage and reading. knitr[@citeKnitr], kableExtra[@citeKableExtra], patchwork[@citePatchwork], gridExtra[@citeGridExtra], grid[@citeGrid], and ggplot2[@citeGgplot2] were used for creating dynamic reports, beautifying table outputs, data visualization, and arranging multiple charts. car[@citeCar] and moments[@citeMoments] were used for model analysis and diagnostics. testthat[@citeTestthat] was used for writing and executing unit tests. styler[@citeStyler] is used for final code formatting.

@@

## Overview {#sec-data_overview}
The dataset comes from FiveThirtyEight's 'Presidential Election Polls (Current Cycle)' [@citeRawData]. FiveThirtyEight is a well-known website recognized for its political, economic, and sports analyses. Its polling aggregation methodology is highly regarded in the field, aiming to provide readers with transparent, scientific, and as accurate as possible predictions. This polling data is compiled from various polling agencies, encompassing a wide range of demographic information, which serves as an essential basis for analyzing public voting preferences in the upcoming presidential election.

In this section, we present the components of the raw data, along with the distribution and summary of key variables. We also detail the data cleaning procedures, evaluate the reliability of the measurements used, and discuss similar datasets.

## Raw data 
The analysis and visualizations in this paper are based on polling results as of October 22. The dataset includes 52 variables, 17,133 samples and 3530 polls from various polling sources. These variables are shown in the below table@tbl-vord.

```{r, fig.height=90, fig.width=90}
#| warning: false
#| message: false
#| echo: false
#| label: tbl-vord
#| tbl-cap: "Varibales of raw data"

# Get the column names and arrange them into multiple columns
column_names <- names(raw_data)
num_columns <- 3 # Set the desired number of columns
num_rows <- ceiling(length(column_names) / num_columns)
matrix_data <- matrix(c(column_names, rep("", num_columns * num_rows - length(column_names))),
  nrow = num_rows, byrow = TRUE
)

# Convert the matrix to a data frame and format it with kable, set font size, and adjust header styling to remove extra row
kable(as.data.frame(matrix_data),
  col.names = NULL
)
```

```{r, fig.height=90, fig.width=90}
#| warning: false
#| message: false
#| echo: false
#| include: false
del_1 <- c("notes", "url", "url_article", "url_topline", "url_crosstab", "source")
droped_data <- raw_data %>% select(-any_of(del_1))
```

We selected 10 variables @tbl-ivatd of interest and their distributions are shown below.
```{r, fig.height=90, fig.width=90}
#| warning: false
#| message: false
#| echo: false
#| label: tbl-ivatd
#| tbl-cap: "Important variables and their descriptions"

variable_descriptions <- data.frame(
  Variable = c(
    "poll_id", "methodology", "population", "ranked_choice_reallocated",
    "hypothetical", "answer", "numeric_grade", "pollscore",
    "transparency_score", "sample_size", "start_date", "end_date", "pct"
  ),
  Description = c(
    "Unique identifier for each poll conducted.",
    "The method used to conduct the poll (e.g., Online Panel).",
    "The abbreviated description of the respondent group, typically indicating their voting status (e.g., 'lv' for likely voters).",
    "Indicates if ranked-choice voting reallocations have been applied in the results.",
    "Indicates whether the poll is about a hypothetical match-up.",
    "The response or answer choice given in the poll (e.g., the candidate's party).",
    "A numeric rating given to the pollster to indicate their quality or reliability (e.g., 3.0).",
    "A numeric value representing the score or reliability of the pollster in question (e.g., -1.1).",
    "A score reflecting the pollster's transparency about their methodology (e.g., 9.0).",
    "The total number of respondents participating in the poll (e.g., 2712).",
    "The date the poll began (e.g., 10/8/24).",
    "The date the poll ended (e.g., 10/11/24).",
    "The percentage of the vote or support that the candidate received in the poll (e.g., 51.0 for Kamala Harris)."
  )
)

# Create the table using kable
kable(variable_descriptions) %>%
  kable_styling() %>%
  column_spec(1, width = "4.5cm") %>% # Adjust the width of the first column
  column_spec(2, width = "10cm") # Adjust the width of the second column
```

```{r}
#| warning: false
#| message: false
#| echo: false
#| include: false
catego <- c(
  "poll_id", "pollster_id", "sponsor_ids", "pollster_rating_id", "methodology", "state",
  "sponsor_candidate_id", "sponsor_candidate_party", "question_id", "population", "tracking", "created_at", "internal",
  "partisan", "race_id", "ranked_choice_reallocated", "ranked_choice_round", "hypothetical", "party", "answer"
)
```

```{r}
#| warning: false
#| message: false
#| echo: false
#| include: false
catego_inp <- c("poll_id", "methodology", "population", "ranked_choice_reallocated", "hypothetical", "answer")
```

The left bar chart in @fig-bv shows the distribution of the `ranked_choice_reallocated` variable. The chart indicates that the majority of the data points are marked as `FALSE`, meaning ranked-choice voting reallocations have not been applied in most cases. Only a very small number of instances are marked as `TRUE`.

The right bar chart in @fig-bv illustrates the distribution of the `hypothetical` variable. It shows that a larger proportion of the data is marked as `TRUE`, indicating that the poll results are often based on hypothetical match-ups. There are fewer instances marked as `FALSE`, where the poll is not hypothetical.

```{r, fig.height= 5, fig.width=10, fig.pos="H"}
#| warning: false
#| message: false
#| echo: false
#| label: fig-bv
#| fig-cap: "Distribution of boolean variables"
plots <- list()
# Create bar charts for 'ranked_choice_reallocated' and 'hypothetical'
plots[["ranked_choice"]] <- ggplot(raw_data, aes(x = ranked_choice_reallocated)) +
  geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
  labs(x = "Ranked Choice Reallocated", y = "Count") +
  theme_minimal(base_size = 15) +
  theme(
    plot.title = element_text(hjust = 0.5, size = 12),
    axis.title = element_text(size = 10),
    axis.text = element_text(size = 10)
  )

plots[["hypothetical"]] <- ggplot(raw_data, aes(x = hypothetical)) +
  geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
  labs(x = "Hypothetical", y = "Count") +
  theme_minimal(base_size = 15) +
  theme(
    plot.title = element_text(hjust = 0.5, size = 12),
    axis.title = element_text(size = 10),
    axis.text = element_text(size = 10)
  )

# Combine and print the plots using patchwork
combined_plot <- wrap_plots(plots, ncol = 2, nrow = 1) +
  plot_annotation(
    theme = theme(
      plot.title = element_text(hjust = 0.5, size = 14)
    )
  )
# Print the combined plot
print(combined_plot)
```

The three charts depict the distribution of key variables in the dataset: `methodology`, `population`, and `answer`. In the most left chart of @fig-cv, we see that the most frequently used polling methodology is "Online Panel," followed by "Live Phone" and "Live Phone/Text-to-Web." The "Online Panel" category significantly outnumbers the others, while the "Other" category also includes a notable count, representing various methodologies grouped together.

The middle chart of @fig-cv shows the distribution of different respondent groups. "lv" (likely voters) and "rv" (registered voters) dominate, with "rv" showing a slightly higher count, indicating that these two groups make up the majority of the sample. Other groups, such as "a" (all adults), "v," and those with missing values ("NA"), represent much smaller portions of the respondent pool.

The most right chart of @fig-cv, `Top 3 Answer and Others`, illustrates the responses given in the polls. "Biden" and "Trump" have similar counts, with "Trump" being slightly higher, while the "Other" category also shows a significant proportion. The response for "Harris" is noticeably lower compared to the others. Overall, these charts provide a visual representation of the polling data, highlighting the dominant methodologies, respondent groups, and response preferences in the dataset.
```{r, fig.pos="H", fig.width=16, fig.height=8}
#| warning: false
#| message: false
#| echo: false
#| label: fig-cv
#| fig-cap: "Distribution of catogorical variables"

plots <- list()
# Find the top 3 most frequent values in 'methodology' and group others as 'Other'
methodology_counts <- sort(table(raw_data$methodology), decreasing = TRUE)
top_3_methodologies <- names(methodology_counts)[1:3]
raw_data$methodology_grouped <- ifelse(raw_data$methodology %in% top_3_methodologies, raw_data$methodology, "Other")
# Create a bar chart for the grouped 'methodology'
plots[["methodology"]] <- ggplot(raw_data, aes(x = methodology_grouped)) +
  geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
  labs(x = "Methodology", y = "Count") +
  theme_minimal(base_size = 15) +
  theme(
    plot.title = element_text(hjust = 0.5, size = 18),
    axis.title = element_text(size = 16),
    axis.text = element_text(size = 16),
    axis.text.x = element_text(angle = 20, hjust = 1)
  )
plots[["population"]] <- ggplot(raw_data, aes(x = population)) +
  geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
  labs(x = "Population", y = "Count") +
  theme_minimal(base_size = 15) +
  theme(
    plot.title = element_text(hjust = 0.5, size = 18),
    axis.title = element_text(size = 16),
    axis.text = element_text(size = 16)
  )
# Find the top 3 most frequent values in 'answer' and group others as 'Other'
answer_counts <- sort(table(raw_data$answer), decreasing = TRUE)
top_3_answer <- names(answer_counts)[1:3]
raw_data$answer <- ifelse(raw_data$answer %in% top_3_answer, raw_data$answer, "Other")
# Create a bar chart for the grouped 'answer'
plots[["answer"]] <- ggplot(raw_data, aes(x = answer)) +
  geom_bar(fill = "#69b3a2", color = "black", alpha = 0.8) +
  labs(x = "Answer", y = "Count") +
  theme_minimal(base_size = 15) +
  theme(
    plot.title = element_text(hjust = 0.5, size = 18),
    axis.title = element_text(size = 16),
    axis.text = element_text(size = 16)
  )
combined_plot <- wrap_plots(plots, ncol = 3, nrow = 1) +
  plot_annotation(
    theme = theme(
      plot.title = element_text(hjust = 0.5, size = 14)
    )
  )
# Print the combined plot
print(combined_plot)
```

```{r}
#| warning: false
#| message: false
#| echo: false
#| include: false
numer <- droped_data %>% select(-any_of(catego))
```
The `numeric_grade` histogram in @fig-donvp1 shows the distribution of a numeric rating assigned to pollsters, representing their overall quality or reliability. The data appear to cluster heavily around scores of 2 and 3, suggesting that a large number of pollsters fall within these quality ranges. The distribution is fairly symmetric, with a noticeable concentration at these higher scores, indicating that most pollsters are considered to be of moderate to good quality.

The `pollscore` histogram in @fig-donvp1 indicates the reliability of each pollster, with lower (more negative) values being better. The distribution shows a peak around zero, with a significant number of pollsters having scores close to zero or slightly negative, and most values being negative, indicating relatively high reliability overall. This implies that most pollsters have moderate to high reliability, with fewer pollsters achieving highly negative scores, which indicate better performance. The tail towards positive values suggests that a small subset of pollsters may have issues with reliability.

The distribution of `transparency_score` in @fig-donvp1 shows a wide spread, with notable peaks at several discrete points, but no clear pattern overall. Higher scores, such as 7.5 and 10, have high frequencies, indicating that some pollsters tend to achieve relatively high transparency. On the other hand, lower scores, such as 2.5 and 5, also show some clustering, but with less consistency.
```{r, fig.pos="H", fig.width=16, fig.height=8}
#| warning: false
#| message: false
#| echo: false
#| label: fig-donvp1
#| fig-cap: "Distribution of numerical varibales part 1"
### Create Plots for Numeric Variables ###
# Create a list to store plots
plots <- list()
# Loop through selected numeric variables and plot their distributions
for (variable in names(numer %>% select(numeric_grade, pollscore, transparency_score))) {
  plots[[variable]] <- ggplot(raw_data, aes_string(x = variable)) +
    geom_histogram(binwidth = 0.5, fill = "#69b3a2", color = "black", alpha = 0.8) +
    labs(x = variable, y = "Frequency") +
    theme_minimal(base_size = 30) +
    theme(
      plot.title = element_text(hjust = 0.5, size = 18),
      axis.title = element_text(size = 16),
      axis.text = element_text(size = 16)
    )
}
### Combine and Print Plots ###
# Combine all individual plots into one using patchwork with 2 columns and 4 rows
combined_plot <- wrap_plots(plots, ncol = 3, nrow = 1) +
  plot_annotation(
    theme = theme(
      plot.title = element_text(hjust = 0.5, size = 14)
    )
  )
# Print the combined plot
print(combined_plot)
```

The `Distribution of sample_size` histogram in @fig-donvp2 illustrates the frequency of poll sample sizes. The majority of polls have relatively small sample sizes, with the frequency decreasing sharply as the sample size increases. The distribution appears highly right-skewed, suggesting that larger sample sizes are much less common than smaller ones.

The `Distribution of pct` histogram in @fig-donvp2 represents the frequency distribution of vote percentages received by candidates in various polls. Most polls have percentage values concentrated around the 30-40% range, with visible peaks at around 0% and 40%. The distribution shows some variation across a wide range but seems to have a higher frequency in the middle range (30-40%) compared to the lower and higher extremes.
```{r, fig.pos="H", fig.width=10, fig.height=6}
#| warning: false
#| message: false
#| echo: false
#| label: fig-donvp2
#| fig-cap: "Distribution of numerical varibales part 2"
### Create Plots for Numeric Variables ###
# Create a list to store plots
plots <- list()
# Loop through selected numeric variables and plot their distributions
for (variable in names(numer %>% select(sample_size, pct))) {
  plots[[variable]] <- ggplot(raw_data, aes_string(x = variable)) +
    geom_histogram(binwidth = 5, fill = "#69b3a2", color = "black", alpha = 0.8) +
    labs(x = variable, y = "Frequency") +
    theme_minimal(base_size = 30) +
    theme(
      plot.title = element_text(hjust = 0.5, size = 12),
      axis.title = element_text(size = 10),
      axis.text = element_text(size = 10)
    )
}
### Combine and Print Plots ###
# Combine all individual plots into one using patchwork with 2 columns and 4 rows
combined_plot <- wrap_plots(plots, ncol = 2, nrow = 1) +
  plot_annotation(
    theme = theme(
      plot.title = element_text(hjust = 0.5, size = 14)
    )
  )
# Print the combined plot
print(combined_plot)
```
